Field-informed Reinforcement Learning for Learnining Large Scale Collective Tasks

### 2023-05-03 paper.tex
chore: minors

\section{Field-informed Reinforcement Learning}
\label{sec:approach}
\ga{Page budget: 2/3 pages \\}
\ga{Plan: we should discuss the approach in detail, including the system model, and the learning dynamics.
Particularly, I would like to highlight how each node in the graph is a local controller,
but it could be seen as a global evolution, therefore we can use global information to inform the local controller.}
\subsection{System model}
\ga{Plan: 
  discussion about typical AC evaluation model, specifying how GNN (with 1-hop information diffusion)
  can be easily integrated with this distributed model
}
\subsection{Learning dynamics}
\ga{
  Plan: discuss the chosen approach, that is Centralised Training and Distributed Execution.
  Particularly, we use DQN in which the neural network is a GNN. So, the dataset consists in a set of graphs,
  where each graph is a snapshot of the system. 
  The target is the Q-value of the action taken in the current state.
  Explain how this can be then used for distributed controllers.
}
\section{Evaluation}
\label{sec:eval}
\ga{Page budget: 2 pages \\}
\ga{Plan: we should discuss the robot aggregation scenario, specifying the state space, the action space, and the reward function.
I dunno if it makes sense to discuss the variants (i.e., fixed area, two areas and moving area). We will see.
}
\subsection{Scenario}

>>>>

\section{Field-informed Reinforcement Learning}
\label{sec:approach}
\ga{Page budget: 2/3 pages \\}
\ga{Plan: we should discuss the approach in detail, including the system model, and the learning dynamics.
Particularly, I would like to highlight how each node in the graph is a local controller,
but it could be seen as a global evolution, therefore we can use global information to inform the local controller.}
\subsection{System model}
\ga{Plan: 
  discussion about the typical AC evaluation model, specifying how GNN (with 1-hop information diffusion)
  can be easily integrated with this distributed model
}
\subsection{Learning dynamics}
\ga{
  Plan: discuss the chosen approach, that is Centralised Training and Distributed Execution.
  Particularly, we use DQN in which the neural network is a GNN. So, the dataset consists in a set of graphs,
  where each graph is a snapshot of the system. 
  The target is the Q-value of the action taken in the current state.
  Explain how this can be then used for distributed controllers.
}
\section{Evaluation}
\label{sec:eval}
\ga{Page budget: 2 pages \\}
\ga{Plan: we should discuss the robot aggregation scenario, specifying the state space, the action space, and the reward function.
I dunno if it makes sense to discuss the variants (i.e., fixed area, two areas and moving area). We will see.
}
\subsection{Scenario}
